### 2023-06-26 manuscript.tex
typo [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/be8675b6907eabfc339d356014312f2b2aa8292e.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/be8675b6907eabfc339d356014312f2b2aa8292e/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5383793295

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/2bddf6d7be9adedcbbfc3d6028a6d845d6e72b0f/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/2bddf6d7be9adedcbbfc3d6028a6d845d6e72b0f}{stain/2022-fdo-paper@2bddf6d}
on June 26, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/be8675b6907eabfc339d356014312f2b2aa8292e/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/be8675b6907eabfc339d356014312f2b2aa8292e}{stain/2022-fdo-paper@be8675b}
on June 26, 2023.
